Code for *Tree-Ring Evidence of Increasing Drought Risks amidst Projected Flood Intensification in the Kabul River Basin (Afghanistan and Pakistan)* by Khan et al. (2022)

### 2022-08-03 paper-code.Rmd
Minor text edits.

First we infill the tree ring data

@@

Calculate bootstrapped correlations

@@

```{r}
# Build final model
sPC <- as.data.table(PC[, 1:2])
lmFit <- PCR_reconstruction(PSepAug, sPC, firstYear, transform = 'none')
set.seed(42)
cvFolds <- make_Z(PSepAug$Qa, frac = 0.25, contiguous = TRUE)
lmCV <- cvPCR(PSepAug, sPC, firstYear, transform = 'none',
              Z = cvFolds, use.robust.mean = FALSE)
```

Performance scores

@@

Final reconstruction with bias correction

@@

Calculate rolling statistics and extract drought events

@@

Mann-Kendall trend test with trend-free prewhitening

@@

Export the reconstruction

>>>>

First we infill the tree ring data.

@@

Calculate bootstrapped correlations.

@@

**Build final model**

```{r}
sPC <- as.data.table(PC[, 1:2])
lmFit <- PCR_reconstruction(PSepAug, sPC, firstYear, transform = 'none')
set.seed(42)
cvFolds <- make_Z(PSepAug$Qa, frac = 0.25, contiguous = TRUE)
lmCV <- cvPCR(PSepAug, sPC, firstYear, transform = 'none',
              Z = cvFolds, use.robust.mean = FALSE)
```

**Performance scores**

@@

Final reconstruction with bias correction.

@@

Calculate rolling statistics and extract drought events.

@@

Mann-Kendall trend test with trend-free pre-whitening.

@@

Export the reconstruction.
